---
title: "Decisions"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup-hide, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(learnr)
```

## Exam Marks
Let's consider the dataset `gradebook2` again. The following code has been run to load the data and the libraries we'll need:

```{r setup, include=TRUE, message = FALSE}
library(tidyverse)

gradebook2 <- read.csv("https://raw.githubusercontent.com/sta238/data/main/gradebook2.csv")
```

We want to compute a $95\%$ confidence interval for the mean of the exam marks. Let's use a few different methods and compare.

### Assume exam marks are normally distributed

Plot the exam marks to see if they look normally distributed. Include a histogram and KDE of the exam marks, along with a layer showing a normal distribution with appropriate arguments. Adjust options (e.g. colour, transparency, line type) and provide informative labels so that the different layers can be easily interpreted. 

```{r plot-exam, exercise=TRUE}

```

Compute the $95\%$ confidence interval, assuming the data generating process for the exam marks follows a normal distribution.
```{r CI-t, exercise=TRUE}

# Compute the confidence interval:
tibble(
  "lower" = ,
  "upper" = 
)
```



### Assume n is sufficiently large 

Compute the $95\%$ confidence interval, assuming the sample size is large enough that the Central Limit Theorem applies.
```{r CI-norm, exercise=TRUE}


# Compute the confidence interval:
tibble(
  "lower" = ,
  "upper" = 
)
```


### No extra assumptions

Use the bootstrap principle to compute the $95\%$ confidence interval.

```{r CI-boot, exercise=TRUE}
set.seed(238)



# Compute the confidence interval:
tibble(
  "lower" = ,
  "upper" = 
)
```



## Times

For this section, I have generated a vector called `times` from an exponential distribution. 

```{r setup-times}
set.seed(238)

times <- rexp(30, rate = 2)
```


### Confidence intervals

Find a $95\%$ confidence interval for the mean, $\mu$, using an appropriate method, and use that to compute a $95\%$ confidence interval for $\lambda$.

```{r CI-mu-lambda, exercise=TRUE, exercise.setup = "setup-times"}
set.seed(238)


CI_mu <- tibble(
  "lower" = ,
  "upper" = 
)

# The confidence interval for the mean:
CI_mu

# The confidence interval for lambda:
tibble( 
  "lower" = 1/CI_mu$upper,
  "upper" = 1/CI_mu$lower
)

```

### Testing claims

Say someone is claiming that the true value of $\lambda$ is 3.5 / hour. 

#### Likelihood ratio test

Use a likelihood ratio test to determine if our data gives any evidence against this claim. Note that you'll need to compute the MLE and the likelihood ratio.

```{r likelihood-ratio, exercise=TRUE, exercise.setup = "setup-times"}

```


#### t-test

Use a bootstrap t-test to determine if our data gives any evidence against this claim.

```{r t-test, exercise=TRUE, exercise.setup = "setup-times"}
set.seed(238)


```






